% Created 2020-12-10 Thu 21:18
% Intended LaTeX compiler: xelatex
\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{minted}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{subcaption}
\usepackage{mathtools}
\usepackage{xfrac}
\usepackage[margin=1.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage{epsf}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{pslatex}
\usepackage{hyperref}
\usepackage[adobe-utopia]{mathdesign}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{textgreek}
\renewcommand*{\textgreekfontmap}{%
{phv/*/*}{LGR/neohellenic/*/*}%
{*/b/n}{LGR/artemisia/b/n}%
{*/bx/n}{LGR/artemisia/bx/n}%
{*/*/n}{LGR/artemisia/m/n}%
{*/b/it}{LGR/artemisia/b/it}%
{*/bx/it}{LGR/artemisia/bx/it}%
{*/*/it}{LGR/artemisia/m/it}%
{*/b/sl}{LGR/artemisia/b/sl}%
{*/bx/sl}{LGR/artemisia/bx/sl}%
{*/*/sl}{LGR/artemisia/m/sl}%
{*/*/sc}{LGR/artemisia/m/sc}%
{*/*/sco}{LGR/artemisia/m/sco}%
}
\makeatletter
\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother
\DeclarePairedDelimiterX{\infdivx}[2]{(}{)}{%
#1\;\delimsize\|\;#2%
}
\newcommand{\infdiv}{D\infdivx}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
\def\Z{\mathbb Z}
\def\R{\mathbb R}
\def\C{\mathbb C}
\def\N{\mathbb N}
\def\Q{\mathbb Q}
\def\noi{\noindent}
\onehalfspace
\author{Sandy Urazayev\thanks{University of Kansas (ctu@ku.edu)}}
\date{320; 12020 H.E.}
\title{Final Project Proposal\\\medskip
\large MATH 596}
\hypersetup{
 pdfauthor={Sandy Urazayev},
 pdftitle={Final Project Proposal},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.3)}, 
 pdflang={English}}
\begin{document}

\maketitle
We live in a rather boring world, full of inconsistencies and patterns that we
fit our lives into. We still love it and try to capture its best shades for safe
storing. Unfortunately, time goes and the sharpness of our pictures and data
speedily fades. My final project would revolve around digital media enhancement
and resolution improvement. 

We have many different pictures from as long as a century ago. However, by the
modern standards, they're all of pretty poor quality. Even more modern ones,
suffer from information and data rotting. I saw a fascinating research that
explored image quality enhancement by using Convolution Neural
Networks. \cite{shi2016realtime} What happens is that we apply a pretty
standard-issue neural network and attach Convolution layers, which are very
common in visual learning applications. By properly reducing the error during
backpropagation and feeding smaller-sized images into the network and giving it
an output of the same image, but bigger sized, we can find such a model that
would be able to find a correlation between them. This would allow us to give a
system a never-seen-before low resolution image and expect a better quality
result. 

\bibliography{proposal}
\bibliographystyle{ieeetr}
\end{document}
